\section{Plan}

For the past four years, I have led the development of the Scratch website and worked on cultivating an online community that has grown to close to 800,000 people.
I have also published work describing the ways people participate, create, collaborate and remix on the Scratch Online Community \citep{monroy-hernandez_scratchr:_2007, monroy-hernandez_empowering_2008, monroy-hernandez_computers_2011, hill_responses_2010, aragon_tale_2009, nickerson_appropriation_2011, brennan_making_2010}.

Over the next few months, I plan to continue analyzing the structural, functional and attitudinal aspects of remixing in Scratch to better understand this specific phenomenon as well as the community at large.
I plan to integrate the findings into a cohesive framework for understanding remixing in a way that can be generalizable to other online remixing communities.

\subsection{Resources}
The technical infrastructure to support the website is in already in place.
In the coming days, I am planning to add two extra servers that will help further scale the website to handle more traffic and that will let me analyze the large corpus of data.
We also have a community manager, an IT consultant and a database specialist on a retainer who are able to assist with this research.
I already have the necessary approvals from COUHES\footnote{Committee On the Use of Humans as Experimental Subjects}.

\subsection{Timeline}
\begin{itemize}
\item May 2011 -- Data aggregation. In the first month, I plan to put together the data sets necessary to answer some research questions described in this document. Much of the data has already been collected, but it needs to be collated in an appropriate format for answering each question.
This phase is also exploratory, which will help tweak the framework in this proposal to better represent the patterns found in the data.
\item May 2011 -- Survey and experiment deployment. Also in the first month, I plan to deploy the necessary design interventions that will help get the necessary data that I do not have already. Most of these experiments are already programmed and just need to be tweaked.
\item June, July 2011 -- Data analysis. I plan to create the necessary visualizations and statistical analyses to examine some research questions outlined in this proposal. Additionally, I will build a set of representative case studies and execute the necessary interviews.
\item August 2011 -- Results. I plan to put together the findings in a structured form, and integrate all the findings into a cohesive document accessible to a broad audience.
\item September 2011 -- Draft -- a first draft of the dissertation.
\item January 2012 -- Defense\footnote{This date might change depending on whether whether I am in non-resident status or not}.
\item February 2012 -- Final version.
\end{itemize}
